Essays in Computational Management Science

### 2018-08-22 autocorrelationPaper/to-include.tex
moving folder

Let $x$ and $y$ be random bitstrings and $n$ be the number of dimensions in the memory; let $x_i$ and $y_i$ be the $i$-th bit of $x$ and $y$, respectively; and $d(x, y)$ be the Hamming distance. Whilst the probability of a shared bit-value between same dimension-bits in two random addresses is $1/2$, an address only activates hard-locations close to it.  Let us call these shared bitvalues a \emph{bitmatch in dimension $i$}.

So, what is the probability of bitmatches given that we know the access radius $r$ between the address and a hard-location?
\bigskip

>>>>

\begin{figure}[h]
\centering
\subfloat[1 sample for each distance $x$ \label{fig:sdm-10000w-table-7-2-1sample} ]{\includegraphics[width=0.5\textwidth]{/././images02/sdm-10000w-table-7-2.png}}
\subfloat[6 samples for each distance $x$ \label{fig:sdm-10000w-table-7-2-6samples} ]{\includegraphics[width=0.5\textwidth]{/././images02/sdm-10000w-table-7-2-6-samples.png}}

\caption{Results generated by the framework diverging from Kanerva's original Figure 7.3. Here we had a 1,000 bit, 1,000,000 hard location SDM with 10,000 random bitstrings written into it, which was also Kanerva's configuration.
\label{fig:sdm-10000w-table-7-2}}
\end{figure}

\bigskip
